---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(slam)
library(Rglpk)
library(Matrix)
```

# rStoryShape

<!-- badges: start -->
<!-- badges: end -->

The `rStoryShape` R package is designed to calculate key storytelling metrics, including speed, volume, and circuitousness, based on the research conducted in the paper titled [How quantifying the shape of stories predicts their success](https://www.pnas.org/doi/epdf/10.1073/pnas.2011695118) by Toubia, O., Berger, J., & Eliashberg (2021) published in the Proceedings of the National Academy of Sciences.

This package provides a set of functions and tools to help you analyze and quantify the shape of stories, allowing you to gain insights into their potential success. Whether you're a researcher, storyteller, or data analyst, `rStoryShape` empowers you to apply storytelling metrics in your work, enhancing your ability to craft and evaluate compelling narratives.

Key features:
- Calculate storytelling speed, volumn, and circuitousness.
- Apply storytelling metrics to assess narrative impact.
- Empower your storytelling research and analysis.

With `rStoryShape`, you can harness the science of storytelling to create more engaging and impactful narratives.

## Installation


To use the `rStoryShape` R package, follow these steps:

### Step 1: Install devtools (if not already installed)

Before you can install `rStoryShape`, you may need to install the `devtools` package if you haven't already. You can do this by running the following command in your R environment:

```r
install.packages("devtools")
```
### Step 2: Install rStoryShape
With devtools installed, you can proceed to install rStoryShape from our GitHub repository. Use the following R code:

```r
devtools::install_github("doublejif/rStoryShape")
```
### Step 3: Download the FastText Embedding File
To make the most of rStoryShape, you'll need to download the fastText embedding file in RData format. This file is quite large (approximately 4.63GB), so make sure you have sufficient disk space. You can download it using the following link:

[Download rStoryShape FastText Embedding File](https://drive.google.com/uc?export=download&id=1Nq--lnyG_9cLdjcjVPe4tVl3nqyIm8WT)

Please keep track of the download path on your local system, as you'll need it during the package usage.

With these steps, you'll be fully equipped to quantify storytelling metrics, gain valuable insights into your narratives, and make the most of rStoryShape for your projects.

### Note: Package Reading Problems

Before using the `rStoryShape` package, ensure that you have the following R packages installed to avoid any reading problems:

```r
library(slam)
library(Rglpk)
library(Matrix)
```

These packages are essential for the proper functioning of rStoryShape and for avoiding any issues when working with storytelling metrics.

## Usage with Your Own Embedding

If you wish to use your own embedding with the `rStoryShape` package, please follow these guidelines:

1. **Data Format**: Ensure that your corpus files are in CSV format. Each CSV file should have a column named "text" (case sensitive) containing the text data you want to analyze.

2. **Embedding Format**: If you intend to use your own embedding, please make sure it follows the standard format as specified [here](https://drive.google.com/uc?export=download&id=1koC_c7U2vXJQyl1jAtUa8W7holN1WmLf). Specifically, the first column in your embedding file should be named "word" (case sensitive).

3. **Embedding File Format**: Your embedding file can be in either CSV or Rdata format (files end with ".csv" or ".Rdata"). Ensure that your embedding data adheres to the required structure.

By following these steps, you can seamlessly use your own embeddings with the `rStoryShape` package, allowing for customized analysis of storytelling metrics.

For more details and examples, refer to the package documentation.


### A Simple Example

```{r example}
library(rStoryShape)
## Read your own embedding. It should be a dataframe with the first column names "word", and follows the embedding metrix (n words * 301 dimensions). Like this:
# word X1 X2 X3 X4 ... X299 X300
#---------------------------------------------
#  a   a1 a2 a3 a4 ... a299 a300
#  ,   b1 b2 b3 b4 ... b299 b300
# ...  .. .. .. .. ...  ..   ..
# the  n1 n2 n3 n4 ... n299 n300

## You could replace the path here with the path you save your embedding
path_for_emb<-"data/ft_model_test.Rdata"
## You could replace the path here with the path you save your corpus
path_for_corpus<-"data/corpus.Rdata"
result<-get_the_data(path_for_corpus, path_for_emb, own_emb=FALSE,type_of_window = "length", window_length = 10)
print(result[,2:ncol(result)])
```


